Scattering Auditory Scenes for Classification: Supervised and Unsupervised Approaches

### 2016-06-27 paper/structureScene.tex
write on temporal integration

\section{Scattering representations}
Scattering transforms are translation-invariant representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

@@

\subsection{Early vs. late integration}
Fine-grained classification of acoustic scenes is only made
possible by integrating signal information over a long temporal context.
A straightforward approach, known as early integration, consists in summarizing the multivariate time series of scattering coefficients

>>>>

\section{Scattering representations \label{sec:scattering}}
Scattering transforms are translation-invariant representations of audio signals which cascade an auditory filterbank and a modulation filterbank, interspersed with complex modulus nonlinearities.
Depending upon the chosen architecture, the modulation filterbank may either be performed solely over the time variable or on both time and frequency.
In this section, we present both the temporal scattering transform and the time-frequency scattering transform.

@@

\subsection{Early vs. late temporal integration}
Owing to the scarcity of salient events in many natural soundscapes, fine-grained classification of auditory scenes is only made
possible by integrating signal information over a long temporal context.
Indeed, whereas a few seconds are often sufficient to recognize a speaker,
a musical instrument, or a genre, it may require up to 30 seconds
to disambiguate auditory scenes which share part of their semantic content, \eg a subway train from a subway station or a quiet street from a park.

A straightforward approach, known as early integration, consists in summarizing the multivariate time series of scattering coefficients over the full duration of the auditory scene, by retaining their average values only.
Going back to the definition of the scattering transform given in section \ref{sec:scattering}, this is equivalent to increasing the support $T$ of the low-pass filter $\boldsymbol{\phi}(t)$ up to infinity.
